---
title: "Freedom Of Press Index"
execute:
  echo: false
---

Imagine being unable to speak freely, to spread information freely, to have your every action monitored. For countries that have a low Freedom Press Index, this is the reality that many journalists have to face. The importance of this index can not be refuted; it speaks to the freedom of speech that a country gives to its citizens. However, global press freedom has been on a decline since 2020, a worrisome trend.

```{r}
#| message: false
#| warning: false
library(dplyr)
library(tidyverse)
library(rnaturalearth)
library(rnaturalearthdata)
library(leaflet)

press <- read.csv("RSB_DataSet.csv")
press$Score <- as.numeric(press$Score)
press <- press |>
          add_row(Ranking = 3, Country = "Greenland", Score = 89.48, Political.Context = 91.95, Economic.Context = 85.17, Legal.Framework = 87.5, Safety.Score = 95, Sociocultural.Context = 87.78,Difference.In.Position.From.2022 = -1)

name_mapping <- c("Türkiye" = "Turkey",
                  "Timor-Leste" = "East Timor",
                  "Czech Republic" = "Czechia",
                  "Tanzania" = "United Republic of Tanzania",
                  "Eswatini" = "eSwatini",
                  "Democratic Republic of Congo" = "Democratic Republic of the Congo",
                  "Congo-Brazzaville" = "Republic of the Congo",
                  "Bosnia-Herzegovina" = "Bosnia and Herzegovina",
                  "Guinea Bissau" = "Guinea-Bissau",
                  "Haïti" = "Haiti",
                  "São Tomé and Príncipe" = "São Tomé and Principe",
                  "Hong Kong" = "Hong Kong S.A.R.",
                  "Morocco / Western Sahara" = "Morocco",
                  "East Timor" = "Timor-Leste",
                  "Czechia" = "Czech Republic",
                  "United States" = "United States of America",
                  "OECS" = "eastern Caribbean States",
                  "T\xfcrkiye" = "Turkey")
press$Country <- recode(press$Country, !!!name_mapping)

world <- ne_countries(scale = "medium", returnclass = "sf")
world <- world |>
          left_join(press, by = c("admin" = "Country"))
```

```{r}
leaflet(world) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~colorNumeric("viridis", Score)(Score),
    weight = 1,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = ~paste("Country: ", admin, 
                   "Score: ", Score, 
                   "Rank: ", Ranking),
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto"
    )
  ) %>%
  addLegend(
    pal = colorNumeric("viridis", NULL),
    values = ~Score,
    opacity = 0.7,
    title = "Press Freedom Index Score",
    position = "bottomright") %>%
  setView(lng = 0, lat = 20, zoom = 2) 
```

